---
title: "8105_yh3555_hw5"
author: "Yuchen Hua"
date: "2022-11-13"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(ggplot2)
library(dbplyr)
library(p8105.datasets)
library(viridis)
```

# Problem 1
```{r}
fulldata = 
    tibble(
    files = list.files("data/data1/"),
    path = str_c("data/data1/", files)
) %>%
  mutate(data = map(path, read.csv)) %>%
  unnest()
```
The data were imported and combined together by tibble functions. A dataframe was created to include all the files in the directory. Path to each file was created. The paths was mapped and the data was imported by "read_csv" function. The result of "map" was unnested in the end. 

```{r}
tidydf = fulldata %>%
  mutate( 
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>%
  mutate(week = as.numeric(week)) %>%
  select(group, subj = files, week, outcome)
```
The data had been wide rather than long, so it should be cleaned up via pivot_longer.


```{r}
tidydf %>%
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) +
  geom_point() +
  geom_path() +
  facet_grid(~group)
```
Plot was created to show individuao data, facted by group. 
 
#  Problem 2
```{r}
homicide = read.csv("./data/data2/homicide-data.csv")
```
There were 52179 cases recorded from 50 cities. There were total 12 variables put into observation. The victim's first and last names were recorded, together with their race, age and sex. 

__
```{r}
homicide = homicide %>%
  mutate(city_state = str_c(city, ",", state))
```

```{r}
total = homicide %>%
  group_by(city_state) %>%
  summarize(total_homicide = n()) %>% 
  arrange(desc(total_homicide))
```

```{r}
unsolved = homicide %>%
  group_by(city_state, disposition) %>%
  filter(! disposition %in% c("Closed by arrest")) %>%
  summarize(unsolved_case = n()) %>%
  arrange(desc(unsolved_case))
```



